---
title: "subgroup function"
author: "Huicong Yu SA20229017(20050)"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{subgroup function}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

__te__ is a simple R package developed to find subgroup from a data with dropout. Four functions are considered, namely , _MissingValue_ (determine whether the function contains missing values), _knn.im_ (use the method of knn to impute the missing value), _naive_ (a missing value processing method for deleting missing values) and _subgroup_ (find the subgroup by different intercept)

## Benchmarking _MissingValue_ and _knn.im_ and _naive_ and _subgroup_

The source R code for _MissingValue_ is as follows:
```{r}
MissingValue<-function(x){
  x<-as.matrix(x)
  m<-nrow(x)
  test<-complete.cases(x)
  n<-nrow(x[test,])
  if(n!=m){
    l<-1
  }else{
    l<-0
  }
  return(l)
}
```
This function aim to determind whether there are missing values. 1 mean: have; 0 mean: NO.

The source R code for _knn.im_ is as follows: 
```{r}
knn.im<-function(data,k){
  return(knnImputation(data = data,k=k,scale=T,meth = "weighAvg"))
}
```
If the previous function return 1, then we need to solve the data. This function chooses one method to imputa the missing values.

The source R code for _naive_ is as follows:  
```{r}
naive<-function(data){
  data<-as.data.frame(data)
  data<-na.omit(data)
  return(data)
}
```
This function chooses to delete all data with missing values.

The source R code for _subgroup_ is as follows:
```{r}
subgroup<-function(y,x,p,m,methods){
  y<-as.matrix(y)
  x<-as.matrix(x)
  n<-nrow(y)
  n2<-ncol(x)
  if((n*p) != n2){
    stop("Error in data:the length of x and y is different")
  }
  u<-numeric(n)
  for (i in 1:n) {
    y<-y[i,]
    x<-x[,(p*i+1-p):(p*i)]
    data<-cbind(y,x)
    if(MissingValue(data)==1){
      if(methods=="naive"){
        data<-naive(data = data)
      }else{
        if(methods=="knn.im"){
          data<-knn.im(data = data,k=10)
        }else{
          stop("Error:don't have this methods")
        }
      }
      data<-as.matrix(data)
      y<-data[,1]
      x<-data[,-1]
    }
    fm<-lm(y~x)
    u[i]<-coef(fm)[1]
  }
  u.unique<-unique(x)
  for (j in 1:length(u.unique)) {
    Group<-which(u==u.unique[j])
    cat("Group",j,"individual",Group)
  }
  print(table(u))
}
```
This function is for find different intercept: group the same intercepts into a subgroup. The length of return varable is the number of subgroup.
